CCVPN: Content Centric Virtual Private Networking

### 2016-12-20 paper/main.tex
adding overhead tables to results section in the paper

@@

To compute the overall network throughput, we consider four content packet sizes ($4096$, $10 \times 4096$, $10^2 \times 4096$, and $10^3 \times 4096$). For each content packet size, we measure the average data-rate for transmissions of 1 to 100,000 different interests issues per consumer. We also vary the number of consumers and producers from 1 to 10 of each. Finally, in addition to the network throughput, we also exhibit the total transmission delay for each of the experiments.

@@

>>>>

\usepackage{multirow}

@@

To compute the overall network throughput, we consider four content packet sizes ($1024$, $10 \times 1024$, $10^2 \times 1024$, and $10^3 \times 1024$). For each content packet size, we measure the average data-rate for transmissions of 1 to 100,000 different interests issues per consumer. We also vary the number of consumers and producers from 1 to 10 of each. Finally, in addition to the network throughput, we also exhibit the total transmission delay for each of the experiments.

@@

\begin{table}[!h]
\centering
\caption{Critical cryptographic operations' processing times}
\label{my-label}
\begin{tabular}{|l|l|l|l|l|}
\hline
           & Encryption           & Decryption           & Encap. & Decap. \\ \hline
P.K. Mode  & \multirow{2}{*}{125$\mu s$} & \multirow{2}{*}{193$\mu s$} & 444$\mu s$           & 449$\mu s$           \\ \cline{1-1} \cline{4-5} 
Symm. Mode &                      &                      & TODO          & TODO          \\ \hline
\end{tabular}
\end{table}

\begin{table}[!h]
\centering
\caption{Encryption and decryption times for different content packet sizes}
\label{my-label}
\begin{tabular}{|l|l|l|}
\hline
Content packet size        & Encryption & Decryption \\ \hline
$1024 \times 10^0$ & 125$\mu s$        & 193$\mu s$        \\ \hline
$1024 \times 10^1$ & 239$\mu s$        & 309$\mu s$        \\ \hline
$1024 \times 10^2$ & 570$\mu s$        & 673$\mu s$        \\ \hline
$1024 \times 10^3$ & 687$\mu s$        & 822$\mu s$        \\ \hline
$1024 \times 10^4$ & 863$\mu s$        & 913$\mu s$        \\ \hline
\end{tabular}
\end{table}
